---
title: "deviation"
author: "Pupso"
date: "7/31/2020"
output: html_document
---

```{r}
source("util.r")
```

```{r}
df_deviation = combine_dfs("/home/ludwig/Bachelorarbeit/voting-protocols/data_cluster/data_dev_votes_per_step/","deviation") %>% 
  mutate(quality_dimensions = factor(quality_dimensions)) %>% 
  filter(user_rating_function == "Konsens")


grouped_deviation = df_deviation %>% 
  mutate(scoring_function = factor(scoring_function)) %>%
  #group_by(scoring_function, init_score, deviation_function, vote_evaluation, gravity)
  group_by(scoring_function, init_score, deviation_function, vote_evaluation,gravity, relevance_gravity, user_rating_function, model_type) %>% 
  dplyr::summarise(area_under_gini = mean(area_under_gini), area_under_ndcg = mean(area_under_ndcg), posts_with_no_views = mean(posts_with_no_views),ρ = mean(ρ), n = n()) 
```
```{r}

df_deviation %>% 
  filter(user_rating_function == "Konsens") %>% 
  #filter(deviation_function == "σ") %>% 
  ggplot_cus() + 
  aes(x = area_under_gini, y = area_under_ndcg, size = posts_with_no_views, color = deviation_function) + 
  geom_point(alpha = 0.1) + 
  facet_wrap(~relevance_gravity) 

```

```{r}
df_deviation %>% 
  mutate(init_score = factor(init_score)) %>% 
  filter(user_rating_function == "Konsens") %>% 
 # filter(deviation_function == "σ") %>% 
  ggplot() +
  aes(x = area_under_gini, y = area_under_ndcg, color = deviation_function,size= posts_with_no_views) + # , color = vote_count, shape = user_rating_function, fill = init_score) + 
  theme(text=element_text(family="Trebuchet MS")) +
  #geom_point(alpha =0.3, data = df_deviation, color = "grey70") + 
  geom_point(alpha = 0.5) + 
  #geom_line(alpha = 0.4) +
  facet_grid(scoring_function~relevance_gravity)
```
```{r}
df_deviation %>% 
 # filter(steps <= 100) %>% 
  filter(user_rating_function == "Konsens") %>% 
  #filter(relevance_gravity == 0) %>% 
  #mutate(steps = factor(steps)) %>% 
  ggplot_cus() +
  aes(x = deviation_function,fill = scoring_function,y = area_under_gini) + 
  #theme(legend.position = "left") + 
 # theme(axis.text.x=element_blank(),axis.ticks.x=element_blank(),) +
  geom_boxplot() + 
  #facet_wrap(~quality_dimensions, ncol = nrow(unique(df_dims[,"quality_dimensions"])))
  facet_grid(~relevance_gravity)

if(s)
{
  ggsave("/home/ludwig/Bachelorarbeit/voting-protocols/plots/dev_gini.png")
}

```
```{r}
df_deviation %>% 
 # filter(steps <= 100) %>% 
  filter(user_rating_function == "Konsens") %>% 
  #filter(relevance_gravity == 0) %>% 
  #mutate(steps = factor(steps)) %>% 
  ggplot_cus() +
  aes(x = deviation_function,fill = scoring_function,y = posts_with_no_views  ) +
  theme(legend.position =  "none") + 
  geom_boxplot() + 
  #facet_wrap(~quality_dimensions, ncol = nrow(unique(df_dims[,"quality_dimensions"])))
  facet_grid(~relevance_gravity)
if(s)
{
  ggsave("/home/ludwig/Bachelorarbeit/voting-protocols/plots/dev_pwnv.png")
}


```
```{r}
df_deviation %>% 
 # filter(steps <= 100) %>% 
  filter(user_rating_function == "Konsens") %>% 
  #filter(relevance_gravity == 0) %>% 
  #mutate(steps = factor(steps)) %>% 
  ggplot_cus() +
  aes(x = deviation_function,fill = scoring_function,y = area_under_ndcg ) + 
  theme(legend.position = "none") + 
  geom_boxplot() +
  #facet_wrap(~quality_dimensions, ncol = nrow(unique(df_dims[,"quality_dimensions"])))
  facet_grid(~relevance_gravity)

if(s)
{
  ggsave("/home/ludwig/Bachelorarbeit/voting-protocols/plots/dev_ndcg.png")
}


```
```{r}
df_deviation %>% 
 # filter(steps <= 100) %>% 
  mutate(quality_dimensions = factor(quality_dimensions)) %>% 
  mutate(steps = factor(steps)) %>% 
  ggplot() +
  aes(fill = scoring_function,y =  area_under_curve) + 
  theme(text=element_text(family="Trebuchet MS")) +
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank(),) +
  geom_boxplot() + 
  facet_wrap(~quality_dimensions)
  #facet_wrap(~steps,ncol = nrow(unique(tmp_df[,"steps"])))

```


```{r}
df_dims %>% 
 # filter(steps <= 100) %>% 
  mutate(steps = factor(steps)) %>% 
  ggplot() +
  aes(color = scoring_function,x=area_under_gini,y =  area_under_ndcg, group = seed, shape = user_rating_function) + 
  theme(text=element_text(family="Trebuchet MS")) +
  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank(),) +
  geom_point(alpha = 0.5) + 
  #geom_line(alpha = 0.3) +
  facet_wrap(~quality_dimensions)
  #facet_wrap(~steps,ncol = nrow(unique(tmp_df[,"steps"])))
